---
title: "R Lesson Part 1"
author: "Noelle Brown"
output: html_document
---
# Intro to R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in Data

Read in the `train_titanic.csv` file.
```{r}
titanic <- read.csv('~/Documents/GA/DSI/Lessons/R/data/train_titanic.csv')
head(titanic)
```

## EDA

How many rows and columns are in this dataset?
```{r}
dim(titanic)
# View(titanic)
```

View just the first 10 items in the Age column.
```{r}
head(titanic$Age, 10)
```

How many missing values are there?
```{r}
# is.null(titanic)
# is.null(titanic$Age)
# which(is.na(titanic$Age))
# 1 = rows, 2 = cols
# apply(X, margin, function)
apply(is.na(titanic), 2, which)
```
Drop Missings.
```{r}
titanic_new <- na.omit(titanic)
```

```{Python}
my_list = [1, 2, 3, 4]

print(my_list[-1])
```

Plot a histogram to see the distribution of the Fare column.
```{r}
hist(titanic_new$Fare,
     main = 'Distribution of Fare',
     xlab = 'Fare',
     col = 'blue')
```

Plot a scatterplot of the Fare vs. Age columns.
```{r}
plot(x = titanic_new$Fare,
     y = titanic_new$Age,
     main = 'Fare vs. Age',
     xlab = 'Fare',
     ylab = 'Age')
```

Display summary statistics of the titanic data.
```{r}
summary(titanic_new)
```

How many females and males were aboard the Titanic? Plot the
frequency of females and males. Be sure to give an accurate title and label the axes.
```{r}
female <- sum(titanic_new$Sex == 'female')
male <- sum(titanic_new$Sex == 'male')

fm <- c(female, male)
barplot(fm,
        main = 'Frequency of females vs. males',
        xlab = 'Sex',
        ylab = 'Frequency',
        names.arg = c('Females', 'Males'),
        col = c('red', 'blue'))
```

Use one apply function to output the means of Age, Fare, and Survival. Make sure the output is a real number for all three means.
```{r}
afs <- data.frame(titanic_new$Age, titanic_new$Fare,
                  titanic_new$Survived)
# apply(X, margin, function)
# 1 is rows, 2 is cols
apply(afs, 2, mean, na.rm=TRUE)
```

Display the column names of the titanic dataframe.
```{r}
colnames(titanic_new)
# colnames(titanic_new) <- c('x', 's', ...)
```

Display the last 5 rows of the titanic dataframe.
```{r}
tail(titanic_new, 5)
```


Function Building: Imagine you have another dataset with the same column names, so you want to create a helper function that you can analyze this dataset and the next. 
 - Create objects for the median Age and the minimum and maximum fares. Make sure to ignore missing values.
- Create a dataframe called report that consists of the above values.
- Change the column names of this dataframe to MedianAge, MinFare, and
MaxFare
- Round the results to 2 digits.
- Finally, run the function on the titanic data to show the output.
```{r}
helper_func <- function(df) {
  medage <- median(df$Age[!is.na(df$Age)])
  minfare <- min(df$Fare[!is.na(df$Fare)])
  maxfare <- max(df$Fare[!is.na(df$Fare)])
  df <- data.frame(medage, minfare, maxfare)
  colnames(df) <- c('MedianAge', 'MinFare', 'MaxFare')
  rounded <- round(df, digits = 2)
  return(rounded)
}
helper_func(titanic_new)
```

## Modeling

Remove unnecessary columns.
```{r}
titanic_data <- titanic_new[ , c('Pclass', 'Sex',
                                 'Age', 'SibSp',
                                 'Parch', 'Fare',
                                 'Embarked')]
```

One-Hot Encode Sex and Embarked columns.
```{r}
# install.packages('caret')
library(caret)
# y ~ X
dmy <- dummyVars(" ~ .", data = titanic_data)
X <- data.frame(predict(dmy, newdata = titanic_data))
head(X)

y <- titanic_new[ , 'Survived']
```

Split into training & testing sets.
```{r}
set.seed(13)
sample <- sample.int(n = nrow(X), size = floor(.8*nrow(X)), replace = FALSE)
Xtrain <- X[sample, ]
Xtest <- X[-sample, ]
ytrain <- y[sample]
ytest <- y[-sample]
```

Fit a logistic regression model.
```{r}
# glm(y~X, family=distribution(link=linkfunction), data)
# binomial distribution
# link = logit
model <- glm(ytrain ~ ., family = binomial(link='logit'),
             data = Xtrain)
```

View the results.
```{r}
summary(model)
```

Score the model.
```{r}
# install.packages('InformationValue')
library(InformationValue)

preds <- predict(model, newdata = Xtest, type = 'response')
optCutOff <- optimalCutoff(ytest, preds)[1]
misClassError(ytest, preds, threshold = optCutOff)
confusionMatrix(ytest, preds, threshold = optCutOff)
plotROC(ytest, preds)
```
