---
title: "R Lesson Part 1"
author: "Noelle Brown"
output: html_document
---
# Intro to R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in Data

Read in the `train_titanic.csv` file.
```{r}
titanic <- read.csv('~/your/path/data/train_titanic.csv')
head(titanic)
```

## EDA

How many rows and columns are in this dataset?
```{r}

```

View just the first 10 items in the Age column.
```{r}

```

How many missing values are there?
```{r}

```

Plot a histogram to see the distribution of the Fare column.
```{r}

```

Plot a scatterplot of the Fare vs. Age columns.
```{r}

```

Display summary statistics of the titanic data.
```{r}

```

How many females and males were aboard the Titanic? Plot the
frequency of females and males. Be sure to give an accurate title and label the axes.
```{r}

```

Use one apply function to output the means of Age, Fare, and Survival. Make sure the output is a real number for all three means.
```{r}

```

Display the column names of the titanic dataframe.
```{r}

```

Display the last 5 rows of the titanic dataframe.
```{r}

```


Function Building: Imagine you have another dataset with the same column names, so you want to create a helper function that you can analyze this dataset and the next. 
 - Create objects for the median Age and the minimum and maximum fares. Make sure to ignore missing values.
- Create a dataframe called report that consists of the above values.
- Change the column names of this dataframe to MedianAge, MinFare, and
MaxFare
- Round the results to 2 digits.
- Finally, run the function on the titanic data to show the output.
```{r}

```

## Modeling

Remove unnecessary columns.
```{r}

```

One-Hot Encode Sex and Embarked columns.
```{r}

```

Split into training & testing sets.
```{r}

```

Fit a logistic regression model.
```{r}

```

View the results.
```{r}

```

Score the model.
```{r}

```
